---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggmapcn

<!-- badges: start -->
<!-- badges: end -->

`ggmapcn` is a `ggplot2` extension package for visualizing China's map with customizable projections and styling. This package includes province-level map data and supports adding mainland borders, coastlines, and buffer areas, making it easy to create geographic visualizations of China.

# Installation

Install the development version of ggmapcn from GitHub with:

``` r
# install.packages("devtools")
devtools::install_github("Rimagination/ggmapcn", force = TRUE)
```

# Usage

## Plotting a Map of China

To plot a map of China with province boundaries, use `geom_mapcn()`:

```{r example1, fig.alt='Province Map'}
library(ggplot2)
library(ggmapcn)

ggplot() +
  geom_mapcn() +
  geom_boundary_cn()+
  theme_minimal()
```

## Custom Projection and Styling

If you want to try the Albers projection, you can customize it.

```{r example2, fig.alt='Basic Map'}
ggplot() +
  geom_mapcn(crs = "+proj=aea +lat_1=25 +lat_2=47 +lat_0=0 +lon_0=105 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs", color = "black", fill = "white", size = 0.7) +
  geom_boundary_cn()+
  theme_bw()
```

## Adding Mainland Borders and Coastlines

Use `geom_boundary_cn()` to add mainland borders and coastlines to the map. You can set colors and line widths for both the mainland and coastline boundaries:

```{r example3, fig.alt='Map with Boundary'}
ggplot() +
  geom_mapcn(fill = NA) +
  geom_boundary_cn(
    mainland_color = "black",
    mainland_size = 0.5,
    coastline_color = "skyblue",
    coastline_size = 0.5
  ) +
  theme_bw()
```

## Adding Buffer Zones

The `geom_buffer_cn()` function adds buffer zones around China’s borders. You can specify buffer distances, colors, and projections. The example below shows buffer zones with varying distances:

```{r example4, fig.alt='Map of China'}
ggplot() +
  geom_buffer_cn(mainland_dist = 40000) +
  geom_buffer_cn(mainland_dist = 20000, fill = "#BBB3D8") +
  geom_mapcn(fill = "white") +
  geom_boundary_cn() +
  theme_bw()
```

## Basic world map in WGS84

This example displays a simple world map using the standard WGS84 geographic coordinate system (EPSG:4326), with country boundaries rendered by `geom_world()`.

```{r example5, fig.alt='Map of world'}
ggplot() +
  geom_world(show_ocean=FALSE) +
  theme_bw()
```

## Data Source

The administrative boundary data for China is sourced from **Tianditu** (https://cloudcenter.tianditu.gov.cn/administrativeDivision/), a national geographic information platform that provides authoritative province-, city-, and county-level divisions. This data has been processed into GeoJSON format to ensure compatibility and ease of use within the package.

The global (world) administrative boundary data, on the other hand, is developed by our team. It has been curated and simplified to support consistent cartographic styling and efficient rendering alongside the China-specific layers.
