---
title: "Adding_Spatial_Data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Adding_Spatial_Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ggmapcn)
```

## Introduction

This vignette introduces two functions in the ggmapcn package: `geom_loc` and `geom_vege_raster`. These functions extend the capabilities of the package for spatial data visualization.

## geom_loc: Adding Spatial Point Data Layer with Color by Grouping

The `geom_loc` function allows you to add spatial point data to a ggplot, supporting both sf and tabular data frames, with color mapping based on a grouping variable.

```{r geom_loc, fig.alt='Sample site'}
# Load the example data provided by the package
data(pollen)

# Create a ggplot with spatial points colored by 'Sample type'
ggplot() +
  geom_loc(
    data = pollen, lon = "Longitude", lat = "Latitude",
    mapping = aes(color = `Sample type`), size = 1, alpha = 0.7
  ) +
  labs(title = "Sample Points on Map")+
  guides(color = guide_none()) +
  theme_bw()
```

## geom_vege_raster: Vegetation Map of China Layer for ggplot2

The `geom_vege_raster` function adds a vegetation raster map of China with color-coded vegetation types to a ggplot.

```{r vegetion map, fig.alt='Vegetation Map of China'}
# Add vegetation raster of China to a ggplot
ggplot() +
  geom_vege_raster() +
  guides(fill = guide_none()) +
  theme_bw()
```
