---
title: "Adding_Spatial_Data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Adding_Spatial_Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ggmapcn)
# Define Azimuthal Equidistant projection centered on China
china_proj <- "+proj=aeqd +lat_0=35 +lon_0=105 +ellps=WGS84 +units=m +no_defs"
```

## Introduction

This vignette introduces two functions in the ggmapcn package: `geom_loc` and `geom_vege_raster`. These functions extend the capabilities of the package for spatial data visualization.

## geom_loc: Adding Spatial Point Data Layer with Color by Grouping

The `geom_loc` function allows you to add spatial point data to a ggplot, supporting both sf and tabular data frames, with color mapping based on a grouping variable.

```{r geom_loc, fig.alt='Sample site'}
# Create a ggplot with spatial points colored by 'Category'
set.seed(123)
data_sim <- data.frame(
   Longitude = runif(100, 80, 120),
   Latitude = runif(100, 28, 40),
   Category = sample(c("Type A", "Type B", "Type C"), 100, replace = TRUE)
   )
ggplot() +
   geom_boundary_cn() +
   geom_loc(
     data = data_sim, lon = "Longitude", lat = "Latitude",
     mapping = aes(color = Category), size = 1, alpha = 0.7
   ) +
   theme_bw()
```

## basemap_vege: Vegetation Map of China Layer for ggplot2

The `basemap_vege` function adds a vegetation raster map of China with color-coded vegetation types to a ggplot.

```{r vegetion map, fig.alt='Vegetation Map of China'}
# Add vegetation raster of China to a ggplot
ggplot() +
  basemap_vege() +
  guides(fill = guide_none()) +
  theme_bw()
```

## basemap_dem: Elevation Map of China Layer for ggplot2

The `basemap_dem` function adds a digital elevation model (DEM) raster map of China as a layer to ggplot2.

```{r dem map, fig.alt='Elevation Map of China'}
# Apply Azimuthal Equidistant projection centered on China
ggplot() +
  basemap_dem(crs = china_proj, within_china = TRUE) +
  geom_boundary_cn(crs = china_proj) +
  tidyterra::scale_fill_hypso_c(
    palette = "dem_print",
    breaks = c(0, 2000, 4000, 6000),
    limits = c(0, 7000)
  ) +
  labs(fill = "Elevation (m)") +
  theme_minimal() +
  theme(legend.position = "bottom")
```
