---
title: "World map overview with geom_world()"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{World map overview with geom_world()}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse   = TRUE,
  comment    = "#>",
  fig.width  = 7,
  fig.height = 4
)

library(ggplot2)
library(ggmapcn)
```

## 1. Introduction

`geom_world()` provides a convenient global base map for `ggplot2`. It comes bundled with country polygons, coastlines, and political/administrative boundaries. 

Key features include:
* **Automatic CRS transformation**: Seamlessly projects data to your desired Coordinate Reference System.
* **Antimeridian splitting**: Handles the "Pacific wrap-around" issue automatically when changing central meridians.
* **Layer control**: Toggles for ocean background and administrative boundaries.

## 2. Basic usage

### 2.1 Default WGS84 map

By default, `geom_world()` plots the map using the WGS84 standard.

```{r basic_map, fig.alt="A standard world map using WGS84 projection with default styling."}
ggplot() +
  geom_world() +
  theme_void()
```

### 2.2 Explicit CRS specification

You can specify the CRS directly within the function.

```{r explicit_crs, fig.alt="A world map explicitly set to EPSG:4326 projection."}
ggplot() +
  geom_world(crs = 4326) +
  coord_sf(crs = 4326) +
  theme_void()
```

### 2.3 Hiding the ocean layer

For a cleaner look, you can remove the blue ocean background and change the land fill color.

```{r hide_ocean, fig.alt="A world map with the blue ocean layer removed, showing grey countries on a white background."}
ggplot() +
  geom_world(
    show_ocean   = FALSE,
    country_fill = "grey90"
  ) +
  theme_minimal()
```

### 2.4 Hiding administrative boundaries

If you only need continental landmasses without internal country borders, set `show_admin_boundaries = FALSE`.

```{r hide_admin, fig.alt="A world map showing continental landmasses without internal country borders."}
ggplot() +
  geom_world(
    show_admin_boundaries = FALSE,
    country_fill          = "white"
  ) +
  theme_minimal()
```

Combining both options creates a minimalist silhouette map:

```{r minimal_map, fig.alt="A minimalist world map showing only land shapes with no ocean or borders."}
ggplot() +
  geom_world(
    show_ocean            = FALSE,
    show_admin_boundaries = FALSE
  ) +
  theme_minimal()
```

## 3. Projections

`geom_world()` shines when working with different map projections. It automatically projects the underlying polygons.

### 3.1 Robinson projection

```{r robinson, fig.alt="A world map using the Robinson projection."}
crs_robin <- "+proj=robin +datum=WGS84"

ggplot() +
  geom_world(crs = crs_robin) +
  coord_sf(crs = crs_robin) +
  theme_void()
```

### 3.2 Robinson projection centred at 150°E

Changing the central meridian (centering the map on the Pacific) is often difficult in standard ggplot2. `geom_world()` handles the polygon splitting automatically.

```{r robin_pacific, fig.alt="A Robinson projection world map centered on the Pacific Ocean (150 degrees East)."}
crs_robin_150 <- "+proj=robin +lon_0=150 +datum=WGS84"

ggplot() +
  geom_world(crs = crs_robin_150) +
  coord_sf(crs = crs_robin_150) +
  theme_void()
```

### 3.3 Geographic CRS with shifted central meridian

```{r wgs84_pacific, fig.alt="A rectangular projection world map centered on 150 degrees East."}
crs_wgs84_150 <- "+proj=longlat +datum=WGS84 +lon_0=150"

ggplot() +
  geom_world(crs = crs_wgs84_150) +
  coord_sf(crs = crs_wgs84_150) +
  theme_void()
```

## 4. Axis labels and gridlines

A common issue with `coord_sf()` is that gridlines appear, but axis labels (coordinates) disappear. This often occurs when:
* `expand = TRUE` extends the map beyond ±180° or ±90°.
* The CRS lacks a geographic datum.
* Solid layers (like the ocean polygon) are drawn *on top* of the panel grid.

**Recommended pattern for reliable axis labels:**
Use `expand = FALSE` inside `coord_sf` and set `panel.ontop = TRUE` in the theme.

```{r axis_labels, fig.alt="A world map with clear longitude and latitude axis labels and gridlines drawn on top of the land layer."}
ggplot() +
  geom_world() +
  coord_sf(
    crs    = 4326,
    expand = FALSE,
    datum  = sf::st_crs(4326)
  ) +
  theme_minimal() +
  theme(panel.ontop = TRUE)
```

## 5. Graticule annotation (meridians & parallels)

`annotation_graticule()` provides precise control over meridians and parallels. Unlike standard gridlines, these are annotation layers that:
* Are generated in WGS84 and transformed to your target CRS.
* Allow for custom line spacing (`lon_step`, `lat_step`) and label placement.

### 5.1 Global WGS84 map with graticules

```{r graticule_global, fig.alt="A world map with custom graticule lines labeled every 60 degrees longitude and 30 degrees latitude."}
ggplot() +
  geom_world() +
  annotation_graticule(
    lon_step     = 60,
    lat_step     = 30,
    label_offset = 5
  ) +
  coord_sf(
    crs    = 4326,
    expand = FALSE,
    datum  = sf::st_crs(4326)
  ) +
  theme_void() +
  theme(panel.ontop = TRUE)
```

### 5.2 Robinson projection

Note how the graticules curve naturally with the projection.

```{r graticule_robin, fig.alt="A Robinson projection map with curved graticule lines."}
crs_robin <- "+proj=robin +datum=WGS84"

ggplot() +
  geom_world(crs = crs_robin) +
  annotation_graticule(
    crs          = crs_robin,
    lon_step     = 30,
    lat_step     = 15,
    label_offset = 3e5
  ) +
  coord_sf(crs = crs_robin) +
  theme_void()
```

### 5.3 Regional China map (clean axis labels)

For regional maps, the recommended pattern is to:
1.  Use `annotation_graticule()` to draw the lines but hide its internal labels (`label_color = NA`).
2.  Use standard `labs()` or `coord_sf` labels for the axes.
3.  Keep the region exact with `expand = FALSE`.

```{r region_cn, fig.alt="A regional map of China and surrounding areas with clean axis labels and specific graticule limits."}
cn_xlim <- c(70, 140)
cn_ylim <- c(0, 60)

ggplot() +
  geom_world() +
  annotation_graticule(
    xlim         = cn_xlim,
    ylim         = cn_ylim,
    crs          = 4326,
    lon_step     = 10,
    lat_step     = 10,
    label_color  = NA,
    label_offset = 1,
    label_size   = 3.5
  ) +
  coord_sf(
    xlim   = cn_xlim,
    ylim   = cn_ylim,
    expand = FALSE
  ) +
  labs(
    x = "Longitude",
    y = "Latitude"
  ) +
  theme_bw()
```

## 6. Highlighting selected countries

You can create "highlight" maps by layering `geom_world()` calls. The first call draws the base (e.g., white), and the second call filters for specific countries to color them.

### 6.1 Highlighting China

```{r highlight_cn, fig.alt="A world map with China highlighted in red."}
ggplot() +
  geom_world(
    country_fill = "white",
    show_frame   = TRUE
  ) +
  geom_world(
    filter_attribute = "SOC",
    filter           = "CHN",
    country_fill     = "red"
  ) +
  theme_void()
```

### 6.2 Highlighting multiple countries

Pass a vector of ISO codes to highlight multiple regions.

```{r highlight_multi, fig.alt="A world map highlighting China, Japan, and South Korea in orange."}
focus <- c("CHN", "JPN", "KOR")

ggplot() +
  geom_world(
    country_fill = "grey95",
    show_frame   = TRUE
  ) +
  geom_world(
    filter_attribute = "SOC",
    filter           = focus,
    country_fill     = "#f57f17"
  ) +
  theme_void()
```

## 7. Summary

This vignette introduced how to:
* Draw global maps using `geom_world()`.
* Control ocean and administrative boundary layers.
* Work with different projections.
* Avoid missing axis labels in `coord_sf()`.
* Add custom meridians/parallels with `annotation_graticule()`.
* Highlight individual or groups of countries.
